---
title: "How to use Mhealthannotator"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use Mhealthannotator}
  %\VignetteEngine{knitr::knitr}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Installing 
```{r eval = FALSE}
devtools::install_github("Sage-Bionetworks/mhealthannotator")
```


### Load Library
```{r setup, eval = FALSE, warning = FALSE}
library(mhealthannotator)
```

### Configuring Synapseclient using Reticulate
Many functions in mhealthannotator use reticulate and the Synapse Python client. See the reticulate documentation for information on how to set R to use a specific version of Python if you don’t want to use the default Python installation on your machine. Whichever Python installation you choose should have synapseclient installed.Because mhealthannotator uses reticulate, it is not compatible with the synapser package.

Documentation for installation can be found [here](https://python-docs.synapse.org/build/html/reticulate.html)

### How-to's:
#### Create Your own Visualization Function:
To create a visualization function, expected input is any parse-able data json, jpeg etc. And output will a filepath to the processed files.

```{r eval=FALSE}
## a good and simple example is to make a function that takes in filepath
## and convert to jpeg if image is png format
visualize_photo <- function(filepath){
    if(tools::file_ext(filepath) == "png"){
        new_filepath <- sub('\\.png$', '.jpg', filepath)
        png_mat <- png::readPNG(filepath)
        jpeg::writeJPEG(png_mat, target = new_filepath, quality = 1)
        file.remove(filepath)
        return(new_filepath)
    }else{
        return(filepath)
    }
}
```

#### Create Configuration File:
To create a config file, the app will accept config.yml files containing key-values pair. As a reference, you can check inst/config.yml for config file template. To check whether you are using the correct and available parameters you can run `mhealthannotator::check_config(PATH_TO_CONFIG)`.

```{r eval=FALSE}
# template to use for config file
default:
    app_url: 'https://shinypro.synapse.org/users/atediarjo/mhealthannotator-oauth/'
    team_id: '3425336'
    synapse_opts:
        output_parent_id: 
            - "syn25614357"
        synapse_tbl_id: 
            - "syn22281748" 
        output_filename: 
            - "psoriasis_plaque_annotations.tsv"
        filehandle_cols:
            - "psoriasisAreaPhoto.jpg"
            - "psoriasisAreaPhoto.png"
        uid: 
            - "recordId" # unique identifier for that file in synapse table
        n_batch: 5
        keep_metadata:
            - "participantId"
            - "createdOn"
        sort_keys:
            - "recordId" # optional
    survey_opts:
        survey_1:
                colname: "PGA"
                type: "radio"
                prompt: "PGA:"
                input_choices:
                    0: 0
                    1: 1
                    2: 2
                    3: 3
                    4: 4
                    Cannot Tell: "Cannot Tell"
        survey_2:
            colname: "erythema"
            type: "checkbox_group"
            prompt: "Erythema:"
            input_choices:
                0: 0
                1: 1
                2: 2
                3: 3
                4: 4
                Cannot Tell: "Cannot Tell"
        survey_3:
            colname: "induration"
            type: "slider"
            prompt: "Induration:"
            input_choices:
                min: 0
                max: 5
                step: 1
        survey_4:
            colname: "scaling"
            type: "slider"
            prompt: "Scaling:"
            input_choices:
                min: 0
                max: 5
                step: 1
    image_opts:
        width: "auto"
        height: "auto"
```


#### Run your App using the config and visualization function:
To run the app, you will only require two parameters, which is the configurations file and your desired function. 

```{r eval=FALSE}
mhealthannotator::run_app(
    config = "config.yml",
    funs = visualize_photo
)
```


#### Additional Notes:
To choose config options other than `default`, you can run:
```{r eval=FALSE}
Sys.setenv(R_CONFIG_ACTTIVE= <parameter_choice>)
```
before running the app. More documentation [here](https://cran.r-project.org/web/packages/config/vignettes/introduction.html)
